Cartograms with Rivers

### 2022-10-26 paper/GHRVis.tex
draft: appendix on QGIS pre-processing
draft: autoref algorithm
draft: evaluation
fix: typos
feat: revised paper

\documentclass{egpubl}
\usepackage{eurovis2021}

@@

@@

\author[Q. Wang \& R. S. Laramee]
{\parbox{\textwidth}{\centering Q. Wang
  and R. S. Laramee
    }
    \\
\parbox{\textwidth}{\centering School of Computer Science, University of Nottingham, UK}
}

\title{Cartograms with Dynamic Features}

@@

\begin{abstract}
Cartograms are hybrid representations of geographical and abstract data based on a value-by-area mapping technique. Based on the Dorling cartogram, the Demers cartogram uses squares instead of circles to represent regions, enabling the comparison of regions in a more intuitive way with a higher screen space utilization. One of the disadvantages of the Dorling cartogram and its variants is that regions may be displaced from their original positions, reducing the legibility, readability, and geographical accuracy. To address that, we propose a novel layout algorithm that integrates dynamic topological features such as rivers into Demers cartograms. We evaluate the proposed layout algorithm through a user study with an application to an Electronic Health Records (EHR) dataset. The results demonstrate that the proposed layout algorithm is able to preserve some of the original properties of the cartogram, while improving the legibility, readability, and geographical accuracy of the cartogram. 
\end{abstract}

@@

\section{Evaluation}

@@

% reset \section command for section title "References"
\let\section=\origsection
\printbibliography

>>>>

\documentclass{egpubl}
\usepackage{eurovis2023}

@@

\newcommand{\algorithmautorefname}{Algorithm}

@@

\author[Q. Wang, K. Xu \& R. S. Laramee]
{\parbox{\textwidth}{\centering Q. Wang, K. Xu
  and R. S. Laramee
    }
    \\
\parbox{\textwidth}{\centering School of Computer Science, University of Nottingham, UK}
}

\title{Cartograms with Rivers}

@@

\begin{abstract}
Cartograms are hybrid representations of geographical and abstract data based on a value-by-area mapping technique. Based on the Dorling cartogram, the Demers cartogram uses squares instead of circles to represent regions, enabling the comparison of regions in a more intuitive way with a higher screen space utilization. One of the disadvantages of the Dorling cartogram and its variants is that regions may be displaced from their original positions, reducing the legibility, readability, and geographical accuracy. To address this, we propose a novel cartogram layout algorithm that integrates dynamic topological features such as rivers into Demers cartograms. Rivers affect both the layout and appearance of cartograms. We evaluate the proposed layout algorithm through a user study with an application to an Electronic Health Records (EHR) dataset. The results demonstrate that the proposed layout algorithm is able to preserve some of the original properties of the cartogram, while improving the legibility, readability, and geographical accuracy of the cartogram. 
\end{abstract}

@@

\input{section/evaluation}

@@

\clearpage
% reset \section command for section title "References"
\let\section=\origsection
\printbibliography

\cleardoublepage

### 2022-10-26 paper/section/data.tex
feat: revised paper

@@

\subsection{Geospatial Data}

Geospatial boundaries, or shapefiles, were obtained from the sources described below.
{
\begin{figure}[tb!]
    \centering
    \includegraphics[width=0.6\columnwidth]{figure/ccg.png}
    \caption{A map of 135 CCGs in England as of 2020, obtained from the Open Geography Portalx \cite{opengeographyportalxOpen} with EPSG:4326 (WGS84 - World Geodetic System) as the Coordinate Reference System (CRS).}
    \label{fig:ccg}
\end{figure}
}

@@

\bobgraph{River Features:} We used OpenStreetMap \cite{openstreetmapRelation} as our data source to obtain shapefiles for River Thames, River Trent, and River Great Ouse in England. These rivers were chosen as they are well-known rivers and pass through regions with dense populations, and provide informative geographical and topological cues.

@@

After acquiring the shapefiles, we used QGIS \cite{qgisWelcome} to manually adjust projections, and convert them into GeoJSON files. Finally, mapshaper \cite{blochMapshaper} is used to merge and convert the GeoJSON files into a TopoJSON \cite{TopoJSON} file. TopoJSON eliminates redundant coordinates in the data, improving the rendering speed of our implementation. See \autoref{table:pre-processing_result} for the pre-processing result.

We describe the above steps in detail in \autoref{app:pre-processing}.

\subsection{EHR Data}

We obtained the Clinical Commissioning Group Outcomes Indicator Set (CCG OIS) from NHS Digital \cite{nhsdigitalClinical}. The OIS is a set of indicators that are used to measure the quality of care and the associated health outcomes in the NHS. Some datasets include:
\begin{itemize}
    \item Under 75 mortality
    \begin{multicols}{2}
        \begin{itemize}
            \item Cardiovascular disease
            \item Respiratory disease
            \item Liver disease
            \item Cancer
        \end{itemize}
    \end{multicols}
    \item Emergency hospital admission
        \begin{itemize}
            \item Stroke
            \item Alcohol-specific admission and readmission
            \item Coronary heart disease
            \item Readmissions within 30 days of discharge
            \item Children with lower respiratory tract infections
        \end{itemize}
\end{itemize}

>>>>

{
\begin{figure}[htb!]
    \centering
    \includegraphics[width=0.6\columnwidth]{figure/ccg.png}
    \caption{A map of 135 CCGs in England as of 2020, obtained from the Open Geography Portalx \cite{opengeographyportalxOpen} with EPSG:4326 (WGS84 - World Geodetic System) as the Coordinate Reference System (CRS).}
    \label{fig:ccg}
\end{figure}
}

@@

\bobgraph{Geospatial Data}

Geospatial boundaries, or shapefiles, were obtained from the sources described here.

@@

\bobgraph{River Features:} We used OpenStreetMap \cite{openstreetmapRelation} as our data source to obtain shapefiles for River Thames, River Trent, and River Great Ouse in England. These rivers were chosen as they are well-known rivers and pass through regions with dense populations, and provide informative geographical and topological cues. Other rivers cloud be chose, including additional and smaller rivers remains future work.

@@

After acquiring the shapefiles, we used QGIS \cite{qgisWelcome} to manually adjust projections, and convert them into GeoJSON files. Finally, mapshaper \cite{blochMapshaper} is used to merge and convert the GeoJSON files into a TopoJSON \cite{TopoJSON} file. TopoJSON eliminates redundant coordinates in the data, improving the rendering speed of our implementation. See \autoref{table:pre-processing_result} on page \pageref{table:pre-processing_result} for the pre-processing result. We describe the above steps in more detail in \autoref{app:pre-processing}.

\bobgraph{EHR Data}

We obtained the Clinical Commissioning Group Outcomes Indicator Set (CCG OIS) from NHS Digital \cite{nhsdigitalClinical}. The OIS is a set of indicators that are used to measure the quality of care and the associated health outcomes in the NHS. Some datasets include:
\begin{itemize}
    \item Under 75 mortality: cardiovascular disease, respiratory disease, liver disease, and cancer
    \item Emergency hospital admission: stroke, alcohol-specific admission and readmission, coronary heart disease, re-admissions within 30 days of discharge, children with lower respiratory tract infections
\end{itemize}

### 2022-10-26 paper/section/introduction.tex
feat: revised paper

@@

Cartograms are representations of hybrid geographical and abstract data based on a value-by-area mapping technique combining statistical and geographical information \cite{dent2009Cartography}. Various styles of cartograms have been proposed and implemented, covering applications such as urban planning \cite{harris2018Mapping, arranz-lopez2021Enduser}, natural hazard forecasting \cite{pappenberger2019Cartograms, park2020Flood}, conservation and environmental planning \cite{galluzzi2018Mapping, rocchini2019Cartogramming}, political and social demographics \cite{breitzman2018Using, alieva2021How}, and public health decision-making \cite{gao2020Visualising, sack2021Visualizing}.

Among the four types of cartograms categorized by \citea{nusrat2016State} (contiguous, non-contiguous, rectangular, and Dorling), a trade-off between types of accuracy is made (See \autoref{table:accuracy}). For this project, we focus on non-contiguous cartograms like Demers cartograms, because they facilitate statistical comparison between regions and they can make good use of screen space. Building on Demers cartograms \cite{ian2002Cartogram}, we introduce and develop novel dynamic topological features, such as rivers, aiming to improve the readability and geographical accuracy without sacrificing statistical accuracy. We implement a new cartographic layout algorithm that includes these topological features into the layout of the nodes representing geographical regions. To minimize geographical errors and make efficient use of screen space, the algorithm also updates the position of rivers to accommodate the node layout. We then apply the algorithm to a real-world case study using an Electronic Health Records (EHR) dataset to evaluate our algorithm. We also present a user study demonstrating its effectiveness.

@@

One of the major challenges involved is how to develop a layout algorithm that handles different shapes. In other words, the layout algorithm is novel because it handles different types of nodes -- rectangular representing regions and polylines representing rivers. Another challenge we overcome in developing the algorithm is to resolve stalemate situations introduced by dynamic topological features while minimizing geographical error.

>>>>

{
    \begin{figure*}[ht!]
        \centering
        \includegraphics[width=0.8\textwidth,keepaspectratio]{figure/UI.png}
        \caption{A screenshot of the software. User options are provided to adjust the size, color mapping, visibility of nodes and rivers. Other options include the ability to control the overlap removal behavior: rivers can be static, dynamic, or constrained.}
        \label{fig:overview}
    \end{figure*}
}

@@

Cartograms are representations of hybrid geographical and abstract data based on a value-by-area mapping combining statistical and geographical information \cite{dent2009Cartography}. Various styles of cartograms have been proposed and implemented, covering applications such as urban planning \cite{harris2018Mapping, arranz-lopez2021Enduser}, natural hazard forecasting \cite{pappenberger2019Cartograms, park2020Flood}, conservation and environmental planning \cite{galluzzi2018Mapping, rocchini2019Cartogramming}, political and social demographics \cite{breitzman2018Using, alieva2021How}, and public health decision-making \cite{gao2020Visualising, sack2021Visualizing}.

Among the four types of cartograms categorized by \citea{nusrat2016State} (contiguous, non-contiguous, rectangular, and Dorling), a trade-off between types of accuracy is made (See \autoref{table:accuracy}). For this project, we focus on non-contiguous cartograms like Demers cartograms, because they facilitate statistical comparison between regions and they can make good use of screen space. Building on Demers cartograms \cite{ian2002Cartogram}, we introduce and develop novel dynamic topological features, such as rivers, aiming to improve the readability and geographical accuracy without sacrificing statistical accuracy. Standard cartograms are composed of uniform shape nodes. As such, this can reduce their legibility. We implement a new cartographic layout algorithm that includes rivers into the layout of the nodes representing geographical regions. To reduce geographical errors and make efficient use of screen space, the algorithm also updates the position of rivers to accommodate the node layout. We then apply the algorithm to a real-world case study using an Electronic Health Records (EHR) dataset to evaluate the result. We also present a user study demonstrating its effectiveness.

@@

The results of the user study indicate that rivers can improve the legibility of cartograms. One of the major challenges involved is how to develop a layout algorithm that handles different shapes. In other words, the layout algorithm is novel because it handles different types of nodes -- rectangular representing regions and polylines representing rivers. Another challenge we overcome in developing the algorithm is to resolve stalemate situations introduced by dynamic topological features while minimizing geographical error.

### 2022-10-26 paper/section/main.tex
feat: revised paper

\section{Cartograms with Dynamic Features}

 {
  \begin{figure}[tb!]
      \centering
      \includegraphics[width=\columnwidth,keepaspectratio]{figure/UI.png}
      \caption{An screenshot of \software. User options are provided to adjust the size, color mapping, visibility of nodes and rivers. Other options include the ability to control the overlap removal behavior: rivers can be static, dynamic, or constrained.}
      \label{fig:overview}
  \end{figure}
 }

 {
  \begin{figure*}[tb!]
      \centering
      \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{figure/flowchart.png}
      \caption{A flowchart illustration of our layout algorithm. See \autoref{fig:flowchart-stalemate} for the flow of processing stalemate. See also \autoref{alg:UpdateLayout} for more detail. For illustration purposes, we show the rendered views alongside the logical views representing the actual computation.}
      \label{fig:flowchart}
  \end{figure*}

  \begin{figure}[tb!]
      \centering
      \includegraphics[width=\columnwidth,keepaspectratio]{figure/flowchart stalemate.png}
      \caption{A flowchart illustration of stalemate processing.}
      \label{fig:flowchart-stalemate}
  \end{figure}
 }

\autoref{alg:UpdateLayout} and \autoref{fig:flowchart} provide an overview of the process.

\bobgraph{Initialization:} We first load and render the CCG geospatial boundaries. For each CCG we compute the centroid and represent it using a square node, $ \node $, with the initial size, $ \nodeSize $. We then load the river shapefiles and render the rivers. Since the vertices of the river in the shapefiles are not in sequential order, we first render the starting vertex, followed by the next closest vertex. This rendering approach enables us to adjust the river resolution as shown in \autoref{fig:river resolution}. We further apply a smoothing logic by removing vertices that are too close to each other.

\bobgraph{Node layout:} The basic algorithm is as follows: we first apply the Fast Node Overlap Removal (FNOR) algorithm that solves the Variable Placement with Separation Constraints (VPSC) problem \cite{dwyer2006fast} in order to remove overlaps. We chose FNOR over other node overlap removal algorithms because FNOR is able to provide spread minimization and node movement minimization while maintaining a good level of global shape preservation \cite{chen2020Node}. We gradually increase the node size by 1 unit at a time to ensure smooth transitions. An increase in $ \nodeSize $ can cause the nodes to overlap. During overlap removal, we compute node trajectories (See \autoref{alg:check river intersection}) and translate nodes to their new position. Nodes that cross a river are translated back to their previous position. If a node oscillates across a river, we process this as a stalemate. This procedure ends when 1) no node overlap is present; 2) no nodes cross a river. We then increase $ \nodeSize $ by one pixel and repeat the algorithm until the max node size $ \nodeSizeMax $ is reached. The gradual size increase process provides stability to the layout and helps minimize geographical error.

\begin{algorithm}[tb!]
    \caption{Procedure to adjust river positions, remove node overlap and prevent nodes from crossing rivers.}\label{alg:UpdateLayout}
    \textbf{Global variables:} \\
    $ \nodeList \gets $ a list of $ \node $ representing CCGs with the following properties: \\
    \-\hspace{1em}  $\nodeListCross \gets $ the number of $ \node $ in $ \nodeList $ that crosses a river \\
    $ \nodeSize \gets $ the current size of all nodes \\
    $ \nodeSizeMax \gets $ the maximum size of a node \\
    $ \riverList \gets $ a list of $ \river $ representing river features \\
    $ \stalemateMax \gets $ the maximum number of iterations indicating a stalemate \\

@@

\begin{algorithm}[tb!]
    \caption{Procedure to translate rivers.}\label{alg:TranslateRiver}
    \textbf{Input:} \\
    $ \nodeList \gets $ a list of $ \node $ representing CCGs \\

@@

\begin{algorithm}[tb!]
    \caption{Procedure to translate node positions.}\label{alg:TranslateNode}

@@

We use rivers as topological boundaries and prevent nodes from crossing them. The resolution of rivers can be adjusted by the user, as shown in \autoref{fig:river resolution}, the number of vertices is reduced from 10,170 to 30. A pixel-level river resolution is not required as Demers cartograms do not need to represent geography at this level of detail. Instead, a resolution that matches the node size is used. Enabling river simplification reduces the number of edge intersection tests that need to be performed. When a node's position changes, we test if the node's trajectory intersects any segment of a river. See \autoref{alg:check river intersection}. A bounding box intersection test between the edge defined by node translation and river edges can be performed to reduce the number of edge intersection tests required.

    {
        \begin{figure}[tb!]
            \centering
            \includegraphics[width=\columnwidth,keepaspectratio]{figure/river_resolution.png}
            \caption{The resolution of rivers can be dynamically adjusted by the user. A shows River Thames at its original resolution with 10,170 edges. B shows the river at a reduced resolution of 49 edges. We further smooth the river by removing vertices in dense areas, as shown in C. The reduced resolution preserves the majority of River Thames' original shape and improves the performance of our river intersection tests.}
            \label{fig:river resolution}
        \end{figure}
    }

% \begin{noindent}
\begin{algorithm}[tb!]
    \caption{Procedure to test if a node's translation path, $ \nodeLineNV $ intersects a river.}\label{alg:check river intersection}
    \textbf{Input:} \\
    $ \nodeLineNV \gets $ the node's translation path \\
    $ \river \gets $ a river feature \\

@@

    {
        \begin{figure}[tb!]
            \centering
            \includegraphics[width=\columnwidth,keepaspectratio]{figure/stalemate.png}
            \caption{A stalemate situation is when a node's translation path $ \nodeVectorCT $ (iteration 1) intersects a river $ \stalemateMax $ times. The node is translated back to its previous position (iteration 2). A stalemate often occurs when the area is congested and the node is unable to translate to a new position without intersecting a river.}
            \label{fig:stalemate}
        \end{figure}
    }

    {
        \begin{figure}[tb!]
            \centering
            \includegraphics[width=\columnwidth,keepaspectratio]{figure/corridor.png}
            \caption{A stalemate occurs when a node's translation path $ \nodeVectorCT $ intersects a river for $ \stalemateMax $ times, as shown in A. To address the issue, we derive a corridor (orange rectangle in E) based on $ \node $ and $ \nodeFNOR $. All nodes within the corridor are translated based on $ \nodeVectorTC $, such that $ \nodeVectorNNn = \nodeVectorNinNinn $. In order to show a clear illustration, we place nodes sparsely in this figure.}
            \label{fig:corridor}
        \end{figure}
    }

@@

\begin{algorithm}[tb!]
    \caption{Procedure to derive a corridor to translate enclosed nodes. We use an SVG canvas, where the point of origin (0,0) is located at the top left corner, with the x-axis extending to the right and the y-axis extending downwards (See \autoref{fig:stalemate}).}\label{alg:derive corridor}

>>>>

\section{Cartograms with Rivers}
{
    \begin{figure}[htb!]
        \centering
        \includegraphics[width=0.7\columnwidth,keepaspectratio]{figure/river_resolution.png}
        \caption{The resolution of rivers can be dynamically adjusted by the user. A shows River Thames at its original resolution with 10,170 edges. B shows the river at a reduced resolution of 49 edges. We further smooth the river by removing vertices in dense areas, as shown in C. The reduced resolution preserves the majority of River Thames' original shape and improves the performance of our river intersection tests.}
        \label{fig:river resolution}
    \end{figure}
}

{
  \begin{figure*}[htb!]
      \centering
      \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{figure/flowchart.png}
      \caption{A flowchart illustration of our layout algorithm. See \autoref{fig:flowchart-stalemate} for the logic of processing a stalemate. See also \autoref{alg:UpdateLayout} in \autoref{sec:{Cartograms with Rivers}} for more detail. For illustration purposes, we show the rendered views alongside the logical views representing the actual computation.}
      \label{fig:flowchart}
  \end{figure*}

  \begin{figure}[htb!]
      \centering
      \includegraphics[width=\columnwidth,keepaspectratio]{figure/flowchart stalemate.png}
      \caption{A flowchart illustration of stalemate processing. See \autoref{subsec:{Detecting Stalemates}}, \autoref{fig:stalemate}, and \autoref{fig:corridor} for more detail.}
      \label{fig:flowchart-stalemate}
  \end{figure}
}

\begin{algorithm}[htb!]
    \caption{Procedure to adjust river positions, remove node overlap and prevent nodes from crossing rivers. See \autoref{sec:{Cartograms with Rivers}}.}\label{alg:UpdateLayout}
    \textbf{Global variables:} \\
    $ \nodeList \gets $ a list of $ \node $ representing CCGs with the following properties: \\
    \-\hspace{1em}  $\nodeListCross \gets $ the number of $ \node $ in $ \nodeList $ that crosses a river \\
    $ \nodeSize \gets $ the current size of all nodes \\
    $ \nodeSizeMax \gets $ the maximum size of a node \\
    $ \riverList \gets $ a list of $ \river $ representing river features \\
    $ \stalemateMax \gets $ the maximum number of iterations indicating a stalemate \\

@@

\autoref{alg:UpdateLayout} and \autoref{fig:flowchart} provide an overview of the cartogram layout process that includes rivers.

\bobgraph{Initialization with Rivers:} We first load and render the CCG geospatial boundaries. For each CCG we compute the centroid and represent it using a square node, $ \node $, with the initial size, $ \nodeSize $. We then load the river shapefiles and render the rivers. Since the vertices of the river in the shapefiles are not in sequential order, we first render the starting vertex, followed by the next nearest vertex. We do not need the original river resolution to incorporate them into cartograms. We reduce their resolution to match that of the cartogram nodes in order to facilitate node-river intersection tests. This rendering approach enables us to adjust the river resolution as shown in \autoref{fig:river resolution}. We further apply smoothing by removing vertices that are too close to each other.

\bobgraph{Node Layout and Overlap Removal:} The basic algorithm is as follows: we first apply the Fast Node Overlap Removal (FNOR) algorithm that solves the Variable Placement with Separation Constraints (VPSC) problem \cite{dwyer2006fast} in order to remove overlaps. We chose FNOR over other node overlap removal algorithms because FNOR is able to provide spread minimization and node movement minimization while maintaining a good level of global shape preservation \cite{chen2020Node}. We gradually increase the node size by 1 unit at a time to ensure smooth transitions. An increase in $ \nodeSize $ can cause the nodes to overlap. During overlap removal, we compute node trajectories (See \autoref{alg:check river intersection}) and translate nodes to their new position. Nodes that cross a river are translated back to their previous position. If a node oscillates across a river, we process this as a stalemate. This procedure ends when 1) no node overlap is present; 2) no nodes cross a river. We then increase $ \nodeSize $ by one pixel and repeat the algorithm until the max node size $ \nodeSizeMax $ is reached. The gradual size increase process provides stability to the layout and helps minimize geographical error.

\begin{algorithm}[htb!]
    \caption{Procedure to translate rivers.}\label{alg:TranslateRiver}
    \textbf{Input:} \\
    $ \nodeList \gets $ a list of $ \node $ representing CCGs \\

@@

\begin{algorithm}[htb!]
    \caption{Procedure to translate node positions.}\label{alg:TranslateNode}

@@

% We use rivers as topological boundaries and prevent nodes from crossing them. The resolution of rivers can be adjusted by the user, as shown in \autoref{fig:river resolution}. In this example, the number of vertices is reduced from 10,170 to 30. A pixel-level river resolution is not required as Demers cartograms do not need to represent geography at this level of detail. Instead, a resolution that matches the node size is used. Enabling river simplification reduces the number of edge intersection tests that need to be performed. %
When a node's position changes, we test if the node's trajectory intersects any segment of a river. See \autoref{alg:check river intersection}. A bounding box intersection test between the edge defined by node translation and river edges can be performed to reduce the number of edge intersection tests required. Using the intersection test, we identify all nodes that cross the river as a result of the initial FNOR algorithm.

\subsection{Translating Rivers}

For all nodes that cross a river, we compute an average vector $ \frac{\riverVector}{count} $ used to translate the corresponding river. See \autoref{alg:TranslateRiver}. This step intends to create room for the next iteration of node translation without crossing a river.

During river translations, some nodes might be crossed by the trajectory of river translations. We move these nodes by the same vector.

% \begin{noindent}
\begin{algorithm}[htb!]
    \caption{Procedure to test if a node's translation path, $ \nodeLineNV $ intersects a river.}\label{alg:check river intersection}
    \textbf{Input:} \\
    $ \nodeLineNV \gets $ the node's translation path \\
    $ \river \gets $ a river feature \\

@@

    {
        \begin{figure}[htb!]
            \centering
            \includegraphics[width=\columnwidth,keepaspectratio]{figure/stalemate.png}
            \caption{A stalemate situation is when a node's translation path $ \nodeVectorCT $ (iteration 1) intersects a river $ \stalemateMax $ times. The node is translated back to its previous position (iteration 2). A stalemate often occurs when the area is congested and the node is unable to translate to a new position without intersecting a river.}
            \label{fig:stalemate}
        \end{figure}
    }

    {
        \begin{figure}[htb!]
            \centering
            \includegraphics[width=\columnwidth,keepaspectratio]{figure/corridor.png}
            \caption{A stalemate occurs when a node's translation path $ \nodeVectorCT $ intersects a river for $ \stalemateMax $ times, as shown in A. To address the issue, we derive a corridor (orange rectangle in E) based on $ \node $ and $ \nodeFNOR $. All nodes within the corridor are translated based on $ \nodeVectorTC $, such that $ \nodeVectorNNn = \nodeVectorNinNinn $. In order to show a clear illustration, we place nodes sparsely in this figure.}
            \label{fig:corridor}
        \end{figure}
    }

@@

\begin{algorithm}[htb!]
    \caption{Procedure to derive a corridor to translate enclosed nodes. We use an SVG canvas, where the point of origin (0,0) is located at the top left corner, with the x-axis extending to the right and the y-axis extending downwards (See \autoref{fig:stalemate}).}\label{alg:derive corridor}
